Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-14 ms.tex
more

Some of the maps in native format are provided in thermodynamic $\delta T$, 
while others are provided in units of MJy/sr. Before performing any fits, 
we convert all measurements to MJy/sr following the guidelines of the document
``HFI-unit conversion and colour correction instructions v1.2''.

@@

% what about the instrumental noise n_{\nu_i} ---> can't find anything
% in planck literature

This error budget is based on \cite{planckdust} Equation 7. $c_{\nu_i}$ is the 
multiplicative calibration uncertainty for the intensity in each band. We 
have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} Table 1. For 
the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from Table 11 of 
\cite{planckcalib}. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:

@@

>>>>

Some of the maps in native format are provided in thermodynamic $\delta T$, 
while others are provided in units of MJy/sr. Before performing any fits, 
we convert all measurements to MJy/sr following the guidelines of \cite{planckresponse} and the document ``HFI-unit conversion and colour correction instructions v1.2''.

%i think it's table 5 that I specifically want to cite within the ``spectral
%response'' paper, but i need to check that those values are consistent
% with the ones i actually used from the other document

@@

% what about the instrumental noise n_{\nu_i} ---> can't find anything
% in planck literature ... nevermind n^2 <-> ii_cov in binary tables

This error budget is the same as that of \cite{planckdust} Equation 7. 
$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
subtracted at the relevant pixel. $\delta0_{\nu_i}$ represents the uncertainty
in the offset used to tie \PLANCK~intensity to HI. We have adopted the 
 $\delta0_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ represents 
the instrumental noise in the pixel of interest, and is taken to be the square 
root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
map. In order to obtain reasonable fitting results at high latitude where the 
data is noisy, we include a prior on $T_2$:

%what about the offset uncertainty for 217 GHz

@@

\subsubsection{Ignoring 217 GHz}
The \cite{planckdust} result used only XX, YY, ZZ, 3000 GHz. When we 
repeat our analysis ignoring 217 GHz, so that we are using the same
set of frequencies, we find that no major changes arise. This actually
should be done/investigated though.
